### 2010-03-18 papers/icfp-2010-desc/paper_desc_levitation.tex
Desc@ICFP: Single column figures, where possible.

Let us examine the consequences of our act. First of all, we discover
that the type theory does not actually need to be extended with the
type former $\EnumU$, the constructors $\NilE$ and $\ConsE$. We have
just defined $\EnumU$ above, by fix-point over the signature functor denoted
by $\ListD$. $\NilE$ and $\ConsE$ are simply the $\ListNil$ and $\ListCons$
constructors of lists.

@@

We shall now fulfil our promises for $\Desc$. We are going to
implement the codes of the universe of descriptions. Interestingly, in
and by itself, the system of codes, $\Desc$, is nothing but a data-type. We
are in the same situation than with $\EnumU$: we ought to be able to describe
the codes of $\Desc$ in $\Desc$ itself. Hence, this code would be a
first-class citizen, born with the standard, generic equipment of
data-types.

@@

\[\stk{
\begin{array}{ll}
\stk{
\data \Desc : \Set \where \\
\;\;\begin{array}{@{}l@{\::\:\:}l@{\quad}l}
    \ldots          & \:\:\ldots \\
    \DHindx         & \PI{H}{\Set} \Desc \To \Desc
\end{array}
}
\vspace{0.2in}
\\
\stk{
\descop{\_\:}{} : \Desc \To \Set \To \Set \\
\begin{array}{@{}l@{\:=\:\:}ll}
\ldots                        &  \ldots \\
\descop{\DHindx{H}{D}}{X}     &  \TIMES{(H \To X)}{\descop{D}{X}}
\end{array}
}
\end{array}
}\]

@@

So, secondly, we have equipped this new data-type with its inherent
structure: the \bind and \return operations. We have been able to
build them as generic functions. Here, we rely on our ability to
compute over descriptions.

>>>>

Let us examine the consequences of our act. First of all, we discover
that the type theory does not actually need to be extended with the
type former $\EnumU$, the constructors $\NilE$ and $\ConsE$. We have
just defined $\EnumU$ above, by fix-point over the signature functor
$\ListD$. $\NilE$ and $\ConsE$ are simply the $\ListNil$ and
$\ListCons$ constructors of lists.

@@

We shall now fulfil our promises for $\Desc$. We are going to
implement the codes of the universe of descriptions. Interestingly, in
and by itself, a code is nothing but a data-type. We are in the same
situation than with $\EnumU$: we ought to be able to describe the
codes of $\Desc$ in $\Desc$ itself. Hence, this code would be a
first-class citizen, born with the standard, generic equipment of
data-types.

@@

\[\stk{
\begin{array}{ll}
\stk{
\data \Desc : \Set \where \\
\;\;\begin{array}{@{}l@{\::\:\:}l@{\quad}l}
    \ldots          & \:\:\ldots \\
    \DHindx         & \PI{H}{Set} \Desc \To \Desc
\end{array}
}
\vspace{0.2in}
\\
\stk{
\descop{\_\:}{} : \Desc \To \Set \To \Set \\
\begin{array}{@{}l@{\:=\:\:}ll}
\ldots                        &  \ldots \\
\descop{\DHindx{H}{D}}{X}     &  \TIMES{(H \To X)}{\descop{D}{X}}
\end{array}
}
\end{array}
}\]

@@

So, secondly, we have equipped this new data-type with its inherent
structure: the \bind and \return operations. We have been able to
build them as generic functions. Here, we rely on our ability to
compute over descriptions, thanks to the induction principle.
